---
title: "Children use disagreement to infer what happened"
author: "Jamie Amemiya, Gail D. Heyman & Tobias Gerstenberg"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
bibliography: grateful-refs.bib
output:
  bookdown::html_document2:
    toc: true
    toc_depth: 4
    toc_float: true
    theme: cosmo
    highlight: tango
---

# Libraries

```{r, message=FALSE, warning=FALSE}
library("lme4")        # for linear mixed effects models
library("rsample")     # for bootstrapping
library("xtable")      # for latex tables
library("kableExtra")  # for rmarkdown
library("knitr")       # for rmarkdown 
library("car")         # for hypothesis test
library("Metrics")     # for rmse
library("scales")      # for percentage plots
library("broom.mixed") # for model summaries
library("grateful")    # for package citations 
library("ggeffects")   # for marginal predictions
library("scales")      # for percentage scales
library("Hmisc")       # for bootstrapped means 
library("ggtext")      # for colored text in ggplot
library("tidyverse")   # for everything else
```

# Helper functions

```{r}
# set classic theme 
theme_set(theme_classic() + 
            theme(text = element_text(size = 16)))

# function for printing out html or latex tables 
print_table = function(data, format = "html", digits = 2){
  if(format == "html"){
    data %>% 
      kable(digits = digits) %>% 
      kable_styling()
  }else if(format == "latex"){
    data %>% 
      xtable(digits = digits,
             caption = "Caption",
             label = "tab:table") %>%
      print(include.rownames = F,
            booktabs = T,
            sanitize.colnames.function = identity,
            caption.placement = "top")
  }
}

# suppress grouping warning 
options(dplyr.summarise.inform = F)

# show figures at the end of code chunks
opts_chunk$set(comment = "",
               fig.show = "hold")

# regression function 
fun.regression = function(formula, data){
  results = glmer(formula = formula,
                  family = binomial,
                  data = data) 
  print(results)
  return(results)
}

# results table 
fun.table = function(results, type = "exploratory"){
  table = results %>% 
    tidy(conf.int = T) %>% 
    filter(effect == "fixed") %>% 
    select(-group)
  
  if (type == "exploratory"){
    table = table %>% 
      select(-c(p.value))
  }
  table %>% 
    print_table()
}

# colors 
l.color = list(agreement = "#89fa50",
               disagreement = "#ff968c",
               ambiguous = "#d38950",
               unambiguous = "#96d5d6")
```

# EXPERIMENT 1

## DATA

### Read in data

```{r, message=FALSE}
# fixed rounding issue; one participant was actually 11 and turned 12 the next day
# participant reported they were 9 despite birth year indicating they were 8; 
# recoded to 9.69 given reported age likely more reliable

df.exp1 = read_csv("../data/data1_infer.csv") %>% 
  rename(trial_order = trial_order_dada) %>%
  mutate(age_continuous = ifelse(age_continuous == 12, 11.99, 
                          ifelse(age_continuous == 8.69, 9.69,
                                 age_continuous)))
```

## STATS

### Counterbalancing

- check if counterbalanced factors moderate the effect of trial type

#### Story order

```{r}
results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_disagree * story_order_wagon + (1 | participant)",
  data = df.exp1)

fun.table(results)
```

#### Trial order

```{r}
results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_disagree * trial_order + (1 | participant)",
  data = df.exp1)

fun.table(results)
```

#### Valence

```{r}
results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_disagree * valence_neg + (1 | participant)",
  data = df.exp1)

fun.table(results)
```

### Confirmatory analysis

#### Trial type effect

Choose ambiguous statement more in disagreement than agreement trials. 

```{r}
results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_disagree + (1 | participant)",
  data = df.exp1)

fun.table(results, type = "confirmatory")
```

#### Inferences above chance

Choose unambiguous in agreement trials above chance (log odds = -.69; 33%). 

```{r}
results = fun.regression(
  formula = "unambiguous_yes ~ 1 + condition_disagree + (1 | participant)",
  data = df.exp1)

fun.table(results, type = "confirmatory")
linearHypothesis(results, "(Intercept) = -.69")
```


#### Ambiguous choice

Choose ambiguous in disagreement trials above chance (log odds = -.69; 33%).

```{r}
results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_agree + (1 | participant)",
  data = df.exp1)

fun.table(results, type = "confirmatory")
linearHypothesis(results, "(Intercept) = -.69")
```

### Exploratory analysis

#### Trial type by age interaction

```{r}
results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_disagree * age_continuous + (1 | participant)",
  data = df.exp1)

fun.table(results)
```

#### Moderation by age

```{r}
# from 7 to 11 years 
for(i in 7:11){
  cat(str_c("Age = ", i, "\n\n"))
  results = fun.regression(
    formula = "ambiguous_yes ~ 1 + condition_disagree + (1 | participant)",
    data = df.exp1 %>% 
      filter(age_group == i))
}
```

## PLOTS

### Inference

```{r fig.height=4, fig.width=8}
set.seed(1)

df.plot.individual = df.exp1 %>% 
    mutate(condition_disagree = as.character(condition_disagree)) %>% 
    group_by(participant, age_continuous, condition_disagree) %>% 
    summarize(pct_amb = sum(ambiguous_yes)/n())

df.age.means = df.plot.individual %>%
  distinct(participant, age_continuous) %>%
  mutate(age_group = floor(age_continuous)) %>%
  group_by(age_group) %>%
  summarize(age_mean = mean(age_continuous),
            n = str_c("n = ", n())) %>%
  ungroup()

df.plot.means = df.exp1 %>% 
  mutate(condition_disagree = as.character(condition_disagree)) %>% 
  group_by(participant, age_group, condition_disagree) %>% 
  summarize(pct_amb = sum(ambiguous_yes)/n()) %>% 
  group_by(age_group, condition_disagree) %>% 
  reframe(response = smean.cl.boot(pct_amb),
          name = c("mean", "low", "high")) %>% 
  left_join(df.age.means,
            by = "age_group") %>% 
  pivot_wider(names_from = name,
              values_from = response) %>% 
  mutate(age_mean = ifelse(condition_disagree == 0, age_mean - 0.05, age_mean + 0.05))

df.plot.text = df.plot.means %>% 
  distinct(age_group, n)

ggplot() + 
  geom_hline(yintercept = 1/3,
             linetype = 2,
             alpha = 0.1) + 
  geom_point(data = df.plot.individual,
             mapping = aes(x = age_continuous,
                           y = pct_amb,
                           color = condition_disagree),
             alpha = 0.5,
             show.legend = T,
             shape = 16,
             size = 1.5) +
  geom_linerange(data = df.plot.means,
                 mapping = aes(x = age_mean,
                               y = mean,
                               ymin = low,
                               ymax = high),
                 color = "gray40") + 
  geom_point(data = df.plot.means,
             mapping = aes(x = age_mean,
                           y = mean,
                           fill = condition_disagree),
             shape = 21,
             size = 3,
             show.legend = T) +
  geom_text(data = df.plot.text,
            mapping = aes(x = age_group + 0.5,
                          y = 1.05,
                          label = n),
            hjust = 0.5) + 
  scale_y_continuous(labels = percent) +
  labs(x = "Age (in years)",
       y = "% Infer Ambiguous Utterance", 
       title = "Experiment 1: Inference") + 
  coord_cartesian(xlim = c(7, 12),
                  ylim = c(0, 1),
                  clip = "off") + 
  scale_color_manual(name = "Trial Type",
                     labels = c("Agreement", "Disagreement"),
                     values = c(l.color$agreement, l.color$disagreement),
                     guide = guide_legend(reverse = T)) +
  scale_fill_manual(name = "Trial Type",
                    labels = c("Agreement", "Disagreement"),
                    values = c(l.color$agreement, l.color$disagreement),
                    guide = guide_legend(reverse = T)) +
  theme(plot.title = element_text(hjust = 0.5,
                                  vjust = 2,
                                  size = 18,
                                  face = "bold"),
        axis.title.y = element_markdown(color = l.color$ambiguous),
        legend.position = "right")

ggsave(filename = "../figures/plots/exp1_inference.pdf",
       width = 8,
       height = 4)
```

# EXPERIMENT 2

## DATA

### Read in data

```{r, message=FALSE}
df.exp2.predict = read_csv("../data/data2_predict.csv")
df.exp2.infer = read_csv("../data/data2_infer.csv") %>% 
  drop_na()
```

## STATS

### Counterbalancing

#### Prediction condition

##### Story order

```{r}
results = fun.regression(
  formula = "dis_yes ~ 1 + condition_amb * story_order_wagon + (1 | participant)",
  data = df.exp2.predict)

fun.table(results)
```

##### Trial order

```{r}
results = fun.regression(
  formula = "dis_yes ~ 1 + condition_amb*trial_order_auau + (1 | participant)",
  data = df.exp2.predict)

fun.table(results)  
```

##### Valence

```{r}
results = fun.regression(
  formula = "dis_yes ~ 1 + condition_amb * valence_neg + (1 | participant)",
  data = df.exp2.predict)

fun.table(results)  
```

#### Inference condition

##### Story order

```{r}
results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_disagree * story_order_wagon + (1 | participant)",
  data = df.exp2.infer)

fun.table(results)  
```

##### Trial order

```{r}
results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_disagree * trial_order_dada + (1 | participant)",
  data = df.exp2.infer)

fun.table(results)  
```

##### Valence

```{r}
results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_disagree * valence_neg + (1 | participant)",
  data = df.exp2.infer)

fun.table(results)  
```

### Confirmatory analyses

#### Trial type effect

##### Prediction condition

Predict disagreement more in ambiguous than unambiguous trials. 

```{r}
results = fun.regression(
  formula = "dis_yes ~ 1 + condition_amb + (1 | participant)",
  data = df.exp2.predict)

prop.table(table(df.exp2.predict$condition_amb, df.exp2.predict$dis_yes),
           margin = 1)

fun.table(results, type = "confirmatory") 
```

##### Inference condition

Choose ambiguous statement more in disagreement than agreement trials. 

```{r}
results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_disagree + (1 | participant)",
  data = df.exp2.infer)

prop.table(table(df.exp2.infer$condition_disagree, df.exp2.infer$ambiguous_yes),
           margin = 1)

fun.table(results, type = "confirmatory") 
```

### Exploratory analysis

#### Trial type by age interaction

##### Prediction

```{r}
results = fun.regression(
  formula = "dis_yes ~ 1 + condition_amb * age_continuous + (1 | participant)",
  data = df.exp2.predict)

fun.table(results) 
```


##### Inference

```{r}
results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_disagree * age_continuous + (1 | participant)",
  data = df.exp2.infer)

fun.table(results) 
```

#### Moderation by age

##### Prediction condition

```{r}
# from 7 to 11 years 
for(i in 7:11){
  cat(str_c("Age = ", i, "\n\n"))
  fun.regression(
    formula = "dis_yes ~ 1 + condition_amb + (1 | participant)",
    data = df.exp2.predict %>% 
      filter(age_group == i))
}
```

##### Inference condition

```{r}
# from 7 to 11 years 
for(i in 7:11){
  cat(str_c("Age = ", i, "\n\n"))
  fun.regression(
    formula = "ambiguous_yes ~ 1 + condition_disagree + (1 | participant)",
    data = df.exp2.infer %>% 
      filter(age_group == i))
}
```

##### Inference condition: First story only

Examine story 1 (trials 1 and 2) and story 4 (trials 7 and 8) among 7-year-olds.

```{r}

# story 1, 7 year olds
df.exp2.infer.7.1 = df.exp2.infer %>%
  filter(age_group == 7 & 
          (trial == "trial 1" |trial == "trial 2"))

results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_disagree + (1 | participant)",
  data = df.exp2.infer.7.1)

prop.table(table(df.exp2.infer.7.1$condition_disagree, df.exp2.infer.7.1$ambiguous_yes),
           margin = 1)

fun.table(results, type = "confirmatory")

# story 4, 7 year olds
df.exp2.infer.7.4 = df.exp2.infer %>%
  filter(age_group == 7 & 
          (trial == "trial 7" |trial == "trial 8"))

results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_disagree + (1 | participant)",
  data = df.exp2.infer.7.4)

prop.table(table(df.exp2.infer.7.4$condition_disagree, df.exp2.infer.7.4$ambiguous_yes),
           margin = 1)

fun.table(results, type = "confirmatory")
```

### Bayesian model

#### Prediction data

```{r}
df.exp2.predict.prob = df.exp2.predict %>% 
  count(age_group, condition_amb_c, dis_yes) %>% 
  group_by(age_group, condition_amb_c) %>% 
  mutate(probability = n/sum(n)) %>% 
  ungroup() %>% 
  mutate(utterance = str_remove_all(condition_amb_c, " Trials"),
         utterance = factor(utterance,
                            levels = c("Unambiguous", "Ambiguous")),
         agreement = factor(dis_yes,
                            levels = c(0, 1),
                            labels = c("agree", "disagree"))) %>% 
  select(-c(condition_amb_c, dis_yes, n)) %>% 
  relocate(probability, .after = last_col()) %>%
  arrange(age_group, utterance, agreement)
```

#### Without softmax

```{r}
utterance_prior = c(0.5, 0.5)

df.inference = df.exp2.predict.prob %>% 
    group_by(agreement, age_group) %>% 
    mutate(prior = utterance_prior) %>% 
    mutate(posterior = probability * prior / 
               sum(probability * prior)) %>% 
    ungroup()

df.model.posterior = df.inference %>% 
    rename(condition = agreement) %>% 
    mutate(condition = factor(condition,
                              levels = c("agree", "disagree"),
                              labels = c("Agreement Trials", "Disagreement Trials"))) %>% 
    filter(utterance == "Ambiguous")
```

#### One temperature parameter

```{r, warning=FALSE, message=FALSE}
age = 7:11

softmax = function(vec, temp = 3) {
    out = exp(vec*temp) / sum(exp(vec*temp))
    return(out)
}

df.data = df.exp2.infer %>% 
    count(age_group, condition_disagree_c, ambiguous_yes) %>% 
    group_by(age_group, condition_disagree_c) %>% 
    reframe(p = n/sum(n)) %>% 
    filter(row_number() %% 2 == 0) %>% 
    rename(agreement = condition_disagree_c) %>% 
    mutate(agreement = ifelse(agreement == "Agreement Trials", "agree", "disagree"))

fit_softmax = function(beta){
    df.prediction = df.inference %>% 
        filter(age_group %in% age) %>%
        select(age_group, utterance, agreement, posterior) %>% 
        pivot_wider(names_from = utterance,
                    values_from = posterior) %>% 
        rowwise() %>% 
        mutate(Unambiguous_soft = softmax(c(Unambiguous, Ambiguous),
                                          temp = beta)[1],
               Ambiguous_soft = softmax(c(Unambiguous, Ambiguous),
                                        temp = beta)[2]) %>% 
        select(age_group, agreement, prediction = Ambiguous_soft)
    
    # compute loss as squared error
    loss = df.data %>% 
        filter(age_group %in% age) %>% 
        left_join(df.prediction) %>% 
        mutate(loss = (p-prediction)^2) %>% 
        pull(loss) %>% 
        sum()
    
    return(loss)
}

# find best fitting softmax parameter
fit = optim(par = 0, 
            fn = fit_softmax)

# use the best parameter
beta = fit[[1]]

# model with softmax 
df.model.softmax = df.inference %>% 
    select(age_group, utterance, agreement, posterior) %>% 
    pivot_wider(names_from = utterance,
                values_from = posterior) %>% 
    rowwise() %>% 
    mutate(Unambiguous_soft = softmax(c(Unambiguous, Ambiguous),
                                      temp = beta)[1],
           Ambiguous_soft = softmax(c(Unambiguous, Ambiguous),
                                    temp = beta)[2]) %>% 
    select(age_group, condition = agreement, posterior = Ambiguous_soft) %>% 
    mutate(condition = factor(condition,
                              levels = c("agree", "disagree"),
                              labels = c("Agreement Trials", "Disagreement Trials")))
```

#### Linear increase of temperature parameter

- fit linear model of softmax temperature as a function of age

```{r}

# rm(beta)

fit_softmax_age = function(par){
  df.prediction = df.inference %>% 
    select(age_group, utterance, agreement, posterior) %>% 
    mutate(beta = par[1] + par[2] * age_group) %>%
    pivot_wider(names_from = utterance,
                values_from = posterior) %>% 
    rowwise() %>% 
    mutate(Unambiguous_soft = softmax(c(Unambiguous, Ambiguous),
                                      temp = beta)[1],
           Ambiguous_soft = softmax(c(Unambiguous, Ambiguous),
                                    temp = beta)[2]) %>% 
    select(age_group, agreement, prediction = Ambiguous_soft)
  
  # compute loss as squared error
  loss = df.data %>% 
    filter(age_group %in% age) %>% 
    left_join(df.prediction,
              by = c("age_group", "agreement")) %>% 
    mutate(loss = (p-prediction)^2) %>% 
    pull(loss) %>% 
    sum()
  
  return(loss)
}

# find best fitting softmax parameter
fit = optim(par = c(0, 0), 
            fn = fit_softmax_age)

df.model.softmax.linear = df.inference %>% 
    select(age_group, utterance, agreement, posterior) %>% 
    pivot_wider(names_from = utterance,
                values_from = posterior) %>% 
    mutate(beta = fit$par[1] + fit$par[2] * age_group) %>%
    rowwise() %>% 
    mutate(Unambiguous_soft = softmax(c(Unambiguous, Ambiguous),
                                      temp = beta)[1],
           Ambiguous_soft = softmax(c(Unambiguous, Ambiguous),
                                    temp = beta)[2]) %>% 
    select(age_group, condition = agreement, posterior = Ambiguous_soft) %>% 
    mutate(condition = factor(condition,
                              levels = c("agree", "disagree"),
                              labels = c("Agreement Trials", "Disagreement Trials")))
```

#### Model comparison

```{r}
df.model.posterior %>% 
    mutate(name = "posterior") %>% 
    select(-c(utterance, probability, prior)) %>% 
    bind_rows(df.model.softmax %>% 
                  mutate(name = "softmax")) %>% 
    bind_rows(df.model.softmax.linear %>% 
                  mutate(name = "softmax increase")) %>% 
    pivot_wider(names_from = name,
                values_from = posterior) %>% 
    left_join(df.data %>% 
                  mutate(condition = factor(agreement,
                                            levels = c("agree", "disagree"),
                                            labels = c("Agreement Trials",
                                                       "Disagreement Trials"))) %>% 
                  select(-agreement),
              by = c("age_group", "condition")) %>% 
    summarize(
        r_posterior = cor(p, posterior),
        r_softmax = cor(p, softmax),
        r_softmaxincrease = cor(p, `softmax increase`),
        rmse_posterior = rmse(p, posterior),
        rmse_softmax = rmse(p, softmax),
        rmse_softmaxincrease = rmse(p, `softmax increase`)) %>% 
    pivot_longer(cols = everything(),
                 names_to = c("index", "name"),
                 names_sep = "_") %>% 
    pivot_wider(names_from = index,
                values_from = value) %>% 
    print_table()
```

## PLOTS

### Prediction

```{r, fig.width=8, fig.height=4}
set.seed(1)

df.plot.individual = df.exp2.predict %>% 
    mutate(condition_amb = as.character(condition_amb)) %>% 
    group_by(participant, age_continuous, condition_amb) %>% 
    summarize(pct_dis = sum(dis_yes)/n()) 

df.age.means = df.plot.individual %>%
  distinct(participant, age_continuous) %>%
  mutate(age_group = floor(age_continuous)) %>%
  group_by(age_group) %>%
  summarize(age_mean = mean(age_continuous),
            n = str_c("n = ", n())) %>%
  ungroup()

df.plot.means = df.exp2.predict %>% 
  mutate(condition_amb = as.character(condition_amb)) %>% 
    group_by(participant, age_group, condition_amb) %>% 
    summarize(pct_dis = sum(dis_yes)/n()) %>% 
  group_by(age_group, condition_amb) %>% 
  reframe(response = smean.cl.boot(pct_dis),
          name = c("mean", "low", "high")) %>% 
  left_join(df.age.means,
            by = "age_group") %>% 
  pivot_wider(names_from = name,
              values_from = response) %>% 
  mutate(age_mean = ifelse(condition_amb == 0, age_mean - 0.05, age_mean + 0.05))

df.plot.text = df.plot.means %>% 
  distinct(age_group, n)


ggplot() + 
  geom_hline(yintercept = 0.5,
             linetype = 2,
             alpha = 0.1) + 
  geom_point(data = df.plot.individual,
             mapping = aes(x = age_continuous,
                           y = pct_dis,
                           color = condition_amb),
             alpha = 0.5,
             show.legend = T,
             shape = 16,
             size = 1.5) +
  geom_linerange(data = df.plot.means,
                 mapping = aes(x = age_mean,
                               y = mean,
                               ymin = low,
                               ymax = high),
                 color = "gray40") + 
  geom_point(data = df.plot.means,
             mapping = aes(x = age_mean,
                           y = mean,
                           fill = condition_amb),
             shape = 21,
             size = 3,
             show.legend = T) +
  geom_text(data = df.plot.text,
            mapping = aes(x = age_group + 0.5,
                          y = 1.05,
                          label = n),
            hjust = 0.5) + 
  scale_y_continuous(labels = percent) +
  labs(x = "Age (in years)",
       y = "% Predict Disagreement", 
       title = "Experiment 2: Prediction") + 
  coord_cartesian(xlim = c(7, 12),
                  ylim = c(0, 1),
                  clip = "off") + 
  scale_color_manual(name = "Trial Type",
                     labels = c("Unambiguous", "Ambiguous"),
                     values = c(l.color$unambiguous, l.color$ambiguous),
                     guide = guide_legend(reverse = T)) +
  scale_fill_manual(name = "Trial Type",
                    labels = c("Unambiguous", "Ambiguous"),
                    values = c(l.color$unambiguous, l.color$ambiguous),
                    guide = guide_legend(reverse = T)) +
  theme(plot.title = element_text(hjust = 0.5,
                                  vjust = 2,
                                  size = 18,
                                  face = "bold"),
        axis.title.y = element_markdown(color = l.color$disagreement),
        legend.position = "right")

ggsave(filename = "../figures/plots/exp2_prediction.pdf",
       width = 8,
       height = 4)
```

### Inference

```{r, fig.width=8, fig.height=4}
set.seed(1)

df.plot.individual = df.exp2.infer %>% 
    mutate(condition_disagree = as.character(condition_disagree)) %>% 
    group_by(participant, age_continuous, condition_disagree) %>% 
    summarize(pct_amb = sum(ambiguous_yes)/n())

df.age.means = df.plot.individual %>%
  distinct(participant, age_continuous) %>%
  mutate(age_group = floor(age_continuous)) %>%
  group_by(age_group) %>%
  summarize(age_mean = mean(age_continuous),
            n = str_c("n = ", n())) %>%
  ungroup()

df.plot.means = df.exp2.infer %>% 
  mutate(condition_disagree = as.character(condition_disagree)) %>% 
  group_by(participant, age_group, condition_disagree) %>% 
  summarize(pct_amb = sum(ambiguous_yes)/n()) %>% 
  group_by(age_group, condition_disagree) %>% 
  reframe(response = smean.cl.boot(pct_amb),
          name = c("mean", "low", "high")) %>% 
  left_join(df.age.means,
            by = "age_group") %>% 
  pivot_wider(names_from = name,
              values_from = response) %>% 
  mutate(age_mean = ifelse(condition_disagree == 0, age_mean - 0.05, age_mean + 0.05))

df.plot.text = df.plot.means %>% 
  distinct(age_group, n)

df.model = df.model.posterior %>% 
    mutate(name = "posterior") %>% 
    select(-c(utterance, probability, prior)) %>% 
    bind_rows(df.model.softmax %>% 
                  mutate(name = "softmax")) %>% 
    bind_rows(df.model.softmax.linear %>% 
                  mutate(name = "softmax increase")) %>% 
  mutate(condition_disagree = factor(condition,
                                     levels = c("Agreement Trials", 
                                                "Disagreement Trials"),
                                     labels = c(0,
                                                1))) %>% 
  left_join(df.age.means %>% 
              select(-n),
            by = "age_group") %>% 
  mutate(age_mean = ifelse(condition_disagree == 0,
                           age_mean - 0.05,
                           age_mean + 0.05))

ggplot() + 
  geom_hline(yintercept = 0.5,
             linetype = 2,
             alpha = 0.1) + 
  geom_point(data = df.plot.individual,
             mapping = aes(x = age_continuous,
                           y = pct_amb,
                           color = condition_disagree),
             alpha = 0.5,
             show.legend = T,
             shape = 16,
             size = 1.5) +
  geom_linerange(data = df.plot.means,
                 mapping = aes(x = age_mean,
                               y = mean,
                               ymin = low,
                               ymax = high),
                 color = "gray40",
                 show.legend = F) + 
  geom_point(data = df.plot.means,
             mapping = aes(x = age_mean,
                           y = mean,
                           fill = condition_disagree),
             shape = 21,
             size = 3,
             show.legend = F) +
  geom_point(data = df.model,
             mapping = aes(x = age_mean,
                           y = posterior,
                           shape = name,
                           fill = condition_disagree),
             size = 1.5,
             alpha = 0.5,
             show.legend = T) +
    geom_text(data = df.plot.text,
            mapping = aes(x = age_group + 0.5,
                          y = 1.05,
                          label = n),
            hjust = 0.5) + 
  scale_y_continuous(labels = percent) +
  labs(x = "Age (in years)",
       y = "% Infer Ambiguous Utterance", 
       title = "Experiment 2: Inference") + 
  coord_cartesian(xlim = c(7, 12),
                  ylim = c(0, 1),
                  clip = "off") + 
  scale_color_manual(name = "Trial Type",
                     labels = c("Agreement", "Disagreement"),
                     values = c(l.color$agreement, l.color$disagreement)) +
  scale_fill_manual(name = "Trial Type",
                    labels = c("Agreement", "Disagreement"),
                    values = c(l.color$agreement, l.color$disagreement)) +
  scale_shape_manual(name = "Model",
                    labels = c("posterior", "softmax", "softmax increase"),
                    values = c(21, 22, 23)) +
  theme(plot.title = element_text(hjust = 0.5,
                                  vjust = 2,
                                  size = 18,
                                  face = "bold"),
        axis.title.y = element_markdown(color = l.color$ambiguous),
        legend.position = "right") +
  guides(fill = guide_legend(override.aes = list(shape = 21,
                                                 size = 3,
                                                 alpha = 1),
                             reverse = T,
                             order = 1),
         shape = guide_legend(override.aes = list(fill = "white",
                                                  alpha = 1)),
         color = "none")

ggsave(filename = "../figures/plots/exp2_inference.pdf",
       width = 8,
       height = 4)
```

# Session info

```{r}
cite_packages(output = "paragraph",
              cite.tidyverse = TRUE,
              out.dir = ".")

sessionInfo()
```