---
title: "Children use disagreement to infer what happened"
author: "Jamie Amemiya, Gail D. Heyman & Tobias Gerstenberg"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_depth: 4
    toc_float: true
    theme: cosmo
    highlight: tango
---

# Libraries

```{r, message=FALSE, warning=FALSE}
library("lme4")        # for linear mixed effects models
library("rsample")     # for bootstrapping
library("xtable")      # for latex tables
library("kableExtra")  # for rmarkdown
library("knitr")       # for rmarkdown 
library("car")         # for hypothesis test
library("Metrics")     # for rmse
library("scales")      # for percentage plots
library("broom.mixed") # for model summaries
library("tidyverse")   # for everything else
```

# Helper functions

```{r}
# function for printing out html or latex tables 
print_table = function(data, format = "html", digits = 2){
  if(format == "html"){
    data %>% 
      kable(digits = digits) %>% 
      kable_styling()
  }else if(format == "latex"){
    data %>% 
      xtable(digits = digits,
             caption = "Caption",
             label = "tab:table") %>%
      print(include.rownames = F,
            booktabs = T,
            sanitize.colnames.function = identity,
            caption.placement = "top")
  }
}

# suppress grouping warning 
options(dplyr.summarise.inform = F)

# show figures at the end of code chunks
opts_chunk$set(comment = "",
               fig.show = "hold")

# regression function 
fun.regression = function(formula, data){
  results = glmer(formula = formula,
                  family = binomial,
                  data = data) 
  print(results)
  return(results)
}

# results table 
fun.table = function(results, type = "exploratory"){
  table = results %>% 
    tidy(conf.int = T) %>% 
    filter(effect == "fixed") %>% 
    select(-group)
  
  if (type == "exploratory"){
    table = table %>% 
      select(-c(p.value))
  }
  table %>% 
    print_table()
}
```

# EXPERIMENT 1

## DATA

### Read in data

```{r, message=FALSE}
df.exp1 = read_csv("../data/data1_infer.csv") %>% 
  rename(trial_order = trial_order_dada)
```

## STATS

### Counterbalancing

- check if counterbalanced factors moderate the effect of trial type

#### Story order

```{r}
results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_disagree * story_order_wagon + (1 | participant)",
  data = df.exp1)

fun.table(results)
```

#### Trial order

```{r}
results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_disagree * trial_order + (1 | participant)",
  data = df.exp1)

fun.table(results)
```

#### Valence

```{r}
results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_disagree * valence_neg + (1 | participant)",
  data = df.exp1)

fun.table(results)
```

### Confirmatory analysis

#### Trial type effect

Choose ambiguous statement more in disagreement than agreement trials. 

```{r}
results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_disagree + (1 | participant)",
  data = df.exp1)

fun.table(results, type = "confirmatory")
```

#### Inferences above chance

Choose unambiguous in agreement trials above chance (log odds = -.69; 33%). 

```{r}
results = fun.regression(
  formula = "unambiguous_yes ~ 1 + condition_disagree + (1 | participant)",
  data = df.exp1)

fun.table(results, type = "confirmatory")
linearHypothesis(results, "(Intercept) = -.69")
```


#### Ambiguous choice

Choose ambiguous in disagreement trials above chance (log odds = -.69; 33%).

```{r}
results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_agree + (1 | participant)",
  data = df.exp1)

fun.table(results, type = "confirmatory")
linearHypothesis(results, "(Intercept) = -.69")
```

### Exploratory analysis

#### Trial type by age interaction

```{r}
results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_disagree * age_continuous + (1 | participant)",
  data = df.exp1)

fun.table(results)
```

#### Moderation by age

```{r}
# from 7 to 11 years 
for(i in 7:11){
  cat(str_c("Age = ", i, "\n\n"))
  results = fun.regression(
    formula = "ambiguous_yes ~ 1 + condition_disagree + (1 | participant)",
    data = df.exp1 %>% 
      filter(age_group == i))
}
```

## PLOTS

### Bar plot

```{r, fig.width=12, fig.height=6}
# Data for Plot
df.plot = df.exp1 %>%
  group_by(condition_disagree) %>%
  count(age_group, selection) %>%
  complete(age_group, selection, fill = list(n = 0)) %>%
  mutate(selection = factor(selection,
                            levels = c("Unambiguous", "Ambiguous", "Random")),
         condition_disagree = factor(condition_disagree,
                                     levels = c(0, 1),
                                     labels = c("Agreement Trials",
                                                "Disagreement Trials")))

# Plot
ggplot(data = df.plot,
         mapping = aes(x = age_group,
                       y = n,
                       fill = selection)) +
  geom_bar(position = "fill",
           stat = "identity",
           color = "black") +
  facet_grid(cols = vars(condition_disagree)) +
  scale_fill_manual(values = c("#009999", "#CC6600", "white")) +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Age", 
       y = "Inferred Utterance",
       fill = "Possible Statements",
       title = "Experiment 1: Inference") + 
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5,
                                  size = 20,
                                  face = "bold"),
        strip.text = element_text(size = 18),
        strip.background = element_blank(),
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 16),
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 16),
        legend.position = "right") 

ggsave(file = "../figures/plots/exp1_figure.pdf",
       width = 12,
       height = 6)
```

# EXPERIMENT 2

## DATA

### Read in data

```{r, message=FALSE}
df.exp2.predict = read_csv("../data/data2_predict.csv")
df.exp2.infer = read_csv("../data/data2_infer.csv") %>% 
  drop_na()
```

## STATS

### Counterbalancing

#### Prediction condition

##### Story order

```{r}
results = fun.regression(
  formula = "dis_yes ~ 1 + condition_amb * story_order_wagon + (1 | participant)",
  data = df.exp2.predict)

fun.table(results)
```

##### Trial order

```{r}
results = fun.regression(
  formula = "dis_yes ~ 1 + condition_amb*trial_order_auau + (1 | participant)",
  data = df.exp2.predict)

fun.table(results)  
```

##### Valence

```{r}
results = fun.regression(
  formula = "dis_yes ~ 1 + condition_amb * valence_neg + (1 | participant)",
  data = df.exp2.predict)

fun.table(results)  
```

#### Inference condition

##### Story order

```{r}
results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_disagree * story_order_wagon + (1 | participant)",
  data = df.exp2.infer)

fun.table(results)  
```

##### Trial order

```{r}
results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_disagree * trial_order_dada + (1 | participant)",
  data = df.exp2.infer)

fun.table(results)  
```

##### Valence

```{r}
results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_disagree * valence_neg + (1 | participant)",
  data = df.exp2.infer)

fun.table(results)  
```

### Confirmatory analyses

#### Trial type effect

##### Prediction condition

Predict disagreement more in ambiguous than unambiguous trials. 

```{r}
results = fun.regression(
  formula = "dis_yes ~ 1 + condition_amb + (1 | participant)",
  data = df.exp2.predict)

prop.table(table(df.exp2.predict$condition_amb, df.exp2.predict$dis_yes),
           margin = 1)

fun.table(results, type = "confirmatory") 
```

##### Inference condition

Choose ambiguous statement more in disagreement than agreement trials. 

```{r}
results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_disagree + (1 | participant)",
  data = df.exp2.infer)

prop.table(table(df.exp2.infer$condition_disagree, df.exp2.infer$ambiguous_yes), margin=1)

fun.table(results, type = "confirmatory") 
```

### Exploratory analysis

#### Trial type by age interaction

##### Prediction

```{r}
results = fun.regression(
  formula = "dis_yes ~ 1 + condition_amb * age_continuous + (1 | participant)",
  data = df.exp2.predict)

fun.table(results) 
```


##### Inference

```{r}
results = fun.regression(
  formula = "ambiguous_yes ~ 1 + condition_disagree * age_continuous + (1 | participant)",
  data = df.exp2.infer)

fun.table(results) 
```

#### Moderation by age

##### Prediction condition

```{r}
# from 7 to 11 years 
for(i in 7:11){
  cat(str_c("Age = ", i, "\n\n"))
  fun.regression(
    formula = "dis_yes ~ 1 + condition_amb + (1 | participant)",
    data = df.exp2.predict %>% 
      filter(age_group == i))
}
```

##### Inference condition

```{r}
# from 7 to 11 years 
for(i in 7:11){
  cat(str_c("Age = ", i, "\n\n"))
  fun.regression(
    formula = "ambiguous_yes ~ 1 + condition_disagree + (1 | participant)",
    data = df.exp2.infer %>% 
      filter(age_group == i))
}
```

### Bootstrapping confidence intervals

#### Prediction condition

```{r, warning=FALSE}
set.seed(1)

# number of bootstrap samples
n_bootstraps = 1000

df.prediction.boot = df.exp2.predict %>% 
  bootstraps(times = n_bootstraps,
             strata = age_group) %>% 
  mutate(prob = map(.x = splits,
                    .f = ~ .x %>% 
                      as_tibble() %>% 
                      count(age_group, condition_amb_c, dis_yes) %>%
                      complete(age_group, condition_amb_c, dis_yes,
                               fill = list(n = 0)) %>% 
                      group_by(age_group, condition_amb_c) %>% 
                      # compute probability
                      reframe(p = n/sum(n)) %>% 
                      arrange(age_group, condition_amb_c) %>% 
                      # keep only even rows
                      filter(row_number() %% 2 == 0))) %>% 
  unnest(prob) %>% 
  select(-splits) %>% 
  group_by(age_group, condition_amb_c) %>% 
  summarize(p_low = quantile(p, 0.025),
            p_high = quantile(p, 0.975)) %>% 
  ungroup()
```

#### Inference condition

```{r, warning=FALSE}
set.seed(1)

# number of bootstrap samples
n_bootstraps = 1000

df.inference.boot = df.exp2.infer %>% 
  bootstraps(times = n_bootstraps,
             strata = age_group) %>% 
  mutate(prob = map(.x = splits,
                    .f = ~ .x %>% 
                      as_tibble() %>% 
                      count(age_group, condition_disagree_c, ambiguous_yes) %>% 
                      complete(age_group, condition_disagree_c, ambiguous_yes,
                               fill = list(n = 0)) %>% 
                      group_by(age_group, condition_disagree_c) %>% 
                      # compute probability
                      reframe(p = n/sum(n)) %>% 
                      arrange(age_group, condition_disagree_c) %>% 
                      # keep only even rows
                      filter(row_number() %% 2 == 0))) %>% 
  unnest(prob) %>% 
  select(-splits) %>% 
  group_by(age_group, condition_disagree_c) %>% 
  summarize(p_low = quantile(p, 0.025),
            p_high = quantile(p, 0.975)) %>% 
  ungroup()
```

### Bayesian model

#### Prediction data

```{r}
df.exp2.predict.prob = df.exp2.predict %>% 
  count(age_group, condition_amb_c, dis_yes) %>% 
  group_by(age_group, condition_amb_c) %>% 
  mutate(probability = n/sum(n)) %>% 
  ungroup() %>% 
  mutate(utterance = str_remove_all(condition_amb_c, " Trials"),
         utterance = factor(utterance,
                            levels = c("Unambiguous", "Ambiguous")),
         agreement = factor(dis_yes,
                            levels = c(0, 1),
                            labels = c("agree", "disagree"))) %>% 
  select(-c(condition_amb_c, dis_yes, n)) %>% 
  relocate(probability, .after = last_col()) %>%
  arrange(age_group, utterance, agreement)
```

#### Without softmax

```{r}
utterance_prior = c(0.5, 0.5)

df.inference = df.exp2.predict.prob %>% 
    group_by(agreement, age_group) %>% 
    mutate(prior = utterance_prior) %>% 
    mutate(posterior = probability * prior / 
               sum(probability * prior)) %>% 
    ungroup()

df.model.posterior = df.inference %>% 
    rename(condition = agreement) %>% 
    mutate(condition = factor(condition,
                              levels = c("agree", "disagree"),
                              labels = c("Agreement Trials", "Disagreement Trials"))) %>% 
    filter(utterance == "Ambiguous")
```

#### One softmax parameter

```{r, warning=FALSE, message=FALSE}
age = 7:11

softmax = function(vec, temp = 3) {
    out = exp(vec*temp) / sum(exp(vec*temp))
    return(out)
}

df.data = df.exp2.infer %>% 
    count(age_group, condition_disagree_c, ambiguous_yes) %>% 
    group_by(age_group, condition_disagree_c) %>% 
    reframe(p = n/sum(n)) %>% 
    filter(row_number() %% 2 == 0) %>% 
    rename(agreement = condition_disagree_c) %>% 
    mutate(agreement = ifelse(agreement == "Agreement Trials", "agree", "disagree"))

fit_softmax = function(beta){
    df.prediction = df.inference %>% 
        filter(age_group %in% age) %>%
        select(age_group, utterance, agreement, posterior) %>% 
        pivot_wider(names_from = utterance,
                    values_from = posterior) %>% 
        rowwise() %>% 
        mutate(Unambiguous_soft = softmax(c(Unambiguous, Ambiguous),
                                          temp = beta)[1],
               Ambiguous_soft = softmax(c(Unambiguous, Ambiguous),
                                        temp = beta)[2]) %>% 
        select(age_group, agreement, prediction = Ambiguous_soft)
    
    # compute loss as squared error
    loss = df.data %>% 
        filter(age_group %in% age) %>% 
        left_join(df.prediction) %>% 
        mutate(loss = (p-prediction)^2) %>% 
        pull(loss) %>% 
        sum()
    
    return(loss)
}

# find best fitting softmax parameter
fit = optim(par = 0, 
            fn = fit_softmax)

# use the best parameter
beta = fit[[1]]

# model with softmax 
df.model.softmax = df.inference %>% 
    select(age_group, utterance, agreement, posterior) %>% 
    pivot_wider(names_from = utterance,
                values_from = posterior) %>% 
    rowwise() %>% 
    mutate(Unambiguous_soft = softmax(c(Unambiguous, Ambiguous),
                                      temp = beta)[1],
           Ambiguous_soft = softmax(c(Unambiguous, Ambiguous),
                                    temp = beta)[2]) %>% 
    select(age_group, condition = agreement, posterior = Ambiguous_soft) %>% 
    mutate(condition = factor(condition,
                              levels = c("agree", "disagree"),
                              labels = c("Agreement Trials", "Disagreement Trials")))
```

#### Separate softmax for each age

```{r, warning=FALSE, message=FALSE}
i = 1
beta.age = numeric()
for (age in 7:11){
    beta.age[i] = optim(par = 0, 
                        fn = fit_softmax)[[1]]
    i = i + 1
}

df.model.softmax.separate = df.inference %>% 
    select(age_group, utterance, agreement, posterior) %>% 
    pivot_wider(names_from = utterance,
                values_from = posterior) %>% 
    group_by(age_group) %>% 
    nest() %>% 
    ungroup() %>% 
    mutate(beta = beta.age) %>% 
    mutate(data = map2(.x = data,
                       .y = beta,
                       .f = ~ .x %>% 
                           rowwise() %>% 
                           mutate(Unambiguous_soft = softmax(c(Unambiguous, Ambiguous),
                                                             temp = .y)[1],
                                  Ambiguous_soft = softmax(c(Unambiguous, Ambiguous),
                                                           temp = .y)[2]))) %>% 
    select(-beta) %>% 
    unnest(data) %>% 
    select(age_group, condition = agreement, posterior = Ambiguous_soft) %>% 
    mutate(condition = factor(condition,
                              levels = c("agree", "disagree"),
                              labels = c("Agreement Trials", "Disagreement Trials")))

```

#### Linear increase in softmax

- fit linear model to the best-fitting softmax parameters 

```{r}
df.beta.linear = tibble(softmax = beta.age) %>% 
    mutate(x = 1:n())

fit = lm(formula = softmax ~ 1 + x,
         data = df.beta.linear)

df.beta.linear = df.beta.linear %>% 
    mutate(prediction = predict(fit))


df.model.softmax.linear = df.inference %>% 
    select(age_group, utterance, agreement, posterior) %>% 
    pivot_wider(names_from = utterance,
                values_from = posterior) %>% 
    group_by(age_group) %>% 
    nest() %>% 
    ungroup() %>% 
    mutate(beta = df.beta.linear$prediction) %>% 
    mutate(data = map2(.x = data,
                       .y = beta,
                       .f = ~ .x %>% 
                           rowwise() %>% 
                           mutate(Unambiguous_soft = softmax(c(Unambiguous, Ambiguous),
                                                             temp = .y)[1],
                                  Ambiguous_soft = softmax(c(Unambiguous, Ambiguous),
                                                           temp = .y)[2]))) %>% 
    select(-beta) %>% 
    unnest(data) %>% 
    select(age_group, condition = agreement, posterior = Ambiguous_soft) %>% 
    mutate(condition = factor(condition,
                              levels = c("agree", "disagree"),
                              labels = c("Agreement Trials", "Disagreement Trials")))
```

#### Model comparison

```{r}
df.model.posterior %>% 
    mutate(name = "posterior") %>% 
    select(-c(utterance, probability, prior)) %>% 
    bind_rows(df.model.softmax %>% 
                  mutate(name = "softmax")) %>% 
    bind_rows(df.model.softmax.linear %>% 
                  mutate(name = "softmax increase")) %>% 
    pivot_wider(names_from = name,
                values_from = posterior) %>% 
    left_join(df.data %>% 
                  mutate(condition = factor(agreement,
                                            levels = c("agree", "disagree"),
                                            labels = c("Agreement Trials",
                                                       "Disagreement Trials"))) %>% 
                  select(-agreement),
              by = c("age_group", "condition")) %>% 
    summarize(
        r_posterior = cor(p, posterior),
        r_softmax = cor(p, softmax),
        r_softmaxincrease = cor(p, `softmax increase`),
        rmse_posterior = rmse(p, posterior),
        rmse_softmax = rmse(p, softmax),
        rmse_softmaxincrease = rmse(p, `softmax increase`)) %>% 
    pivot_longer(cols = everything(),
                 names_to = c("index", "name"),
                 names_sep = "_") %>% 
    pivot_wider(names_from = index,
                values_from = value) %>% 
    print_table()
```


## PLOTS

### Prediction condition

```{r, fig.width=12, fig.height=6, warning=FALSE}
# data for plot 
df.plot = df.exp2.predict %>%
    group_by(condition_amb_c) %>%
    count(age_group, dis_yes) %>%
    complete(age_group, dis_yes,
             fill = list(n = 0)) %>%
    mutate(prediction = factor(dis_yes,
                               levels = c(0, 1),
                               labels = c("Agree", "Disagree"))) %>%
    mutate(condition_amb_c = factor(condition_amb_c,
                                  levels = c("Unambiguous Trials", "Ambiguous Trials"))) %>% 
  ungroup()

df.plot.boot <- df.prediction.boot %>% 
  mutate(condition_amb_c = factor(condition_amb_c,
                                  levels = c("Unambiguous Trials", "Ambiguous Trials")))

# plot
ggplot(data = df.plot,
       mapping = aes(x = age_group,
                     y = n,
                     fill = prediction)) +
  geom_bar(position = "fill",
           stat = "identity",
           color = "black") +
  geom_linerange(data = df.plot.boot,
                 mapping = aes(y = 1,
                               ymin = p_low,
                               ymax = p_high,
                               fill = NA,
                               x = age_group)) +
  facet_grid(cols = vars(condition_amb_c),
             scales = "free") +
  scale_fill_manual(values = c("#A4F76A", "#EEA49A")) +
  scale_y_continuous(labels = percent) +
  labs(x = "Age", 
       y = "Predicted Outcome",
       fill = "Possible Outcomes") + 
  ggtitle("Experiment 2: Prediction") +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5, size = 20, face = "bold"),
        strip.text = element_text(size = 18),
        strip.background = element_blank(),
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 16),
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 16),
        legend.position = "right") 

ggsave(file = "../figures/plots/exp2_pred.pdf",
       width = 12,
       height = 6)
```

### Inference condition

```{r, fig.width=12, fig.height=6, warning=FALSE}
# Data for Inference Plot
df.plot.infer <- df.exp2.infer %>%
  filter(!is.na(ambiguous_yes)) %>%
  rename(condition = condition_disagree_c) %>% 
  mutate(condition = factor(condition, levels = c("Agreement Trials",
                                                  "Disagreement Trials"))) %>% 
  group_by(condition) %>%
  count(age_group, ambiguous_yes) %>%
  complete(age_group, ambiguous_yes, fill = list(n = 0)) %>%
  mutate(selection = factor(ambiguous_yes,
                            levels = c(0, 1),
                            labels = c("Unambiguous", "Ambiguous"))) %>% 
  ungroup()

# Models 
df.model = df.model.posterior %>% 
    mutate(name = "posterior") %>% 
    select(-c(utterance, probability, prior)) %>% 
    bind_rows(df.model.softmax %>% 
                  mutate(name = "softmax")) %>% 
    bind_rows(df.model.softmax.linear %>% 
                  mutate(name = "softmax increase"))

# Bootstrapped confidence intervals
df.inference.boot = df.inference.boot %>% 
  rename(condition = condition_disagree_c) %>% 
  mutate(condition = factor(condition, levels = c("Agreement Trials",
                                                  "Disagreement Trials"))) %>% 
  ungroup()
  

# Plot
ggplot(data = df.plot.infer,
       mapping = aes(x = age_group,
                     y = n,
                     fill = selection)) +
  geom_bar(position = "fill",
           stat = "identity",
           color = "black") +
  geom_linerange(data = df.inference.boot,
                 mapping = aes(y = 1,
                               ymin = p_low,
                               ymax = p_high,
                               fill = NA,
                               x = age_group)) +
  geom_point(data = df.model,
             mapping = aes(x = age_group,
                           y = posterior,
                           fill = NA,
                           shape = name,
                           group = name),
             position = position_dodge(width = 0.9), 
             size = 4,
             fill = "white",
             color = "black") + 
  facet_grid(cols = vars(condition),
             scales = "free") +
  scale_fill_manual(values = c(Unambiguous = "#009999", Ambiguous = "#CC6600"),
                    breaks = c("Unambiguous", "Ambiguous")) +
  scale_shape_manual(values = 21:23) +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Age", 
       y = "Inferred Utterance",
       fill = "Possible Statements",
       shape = "Model",
       title = "Experiment 2: Inference") + 
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5, size = 20, face = "bold"),
        strip.text = element_text(size = 18),
        strip.background = element_blank(),
        axis.title = element_text(size = 18),
        axis.text = element_text(size = 16),
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 16),
        legend.position = "right") 

ggsave(str_c("../figures/plots/exp2_infer_models.pdf"),
       width = 12,
       height = 6)
```
